A-maze of Natural Stories: Texts are comprehensible using the Maze task

### 2022-08-11 Papers/Paper/manuscript.Rmd
Roger starting to edit ms

Behavioral measures of word-by-word reading time provide experimental evidence to test theories of language processing. Maze is a potentially promising method, and it's feasibility has recently increased due to the introduction of A-Maze [@boyceMazeMadeEasy2020]. We tested A-maze on a naturalistic corpora to learn whether participants could understand stories read in the demanding Maze task and whether the reaction time profiles from the Maze task matched those from other methods. To provide context, we first lay out the role of incremental processing methods in theory testing, describe a few common methods, and review some key influences on reading time.

>>>>

Two chief results of human language processing research are that comprehension is highly incremental and that comprehension difficulty is differential and localized. Incrementality in comprehension means that our minds do not wait for large stretches of linguistic input to accrue; rather, we eagerly analyze each moment of input and rapidly integrate it into context [@marslen-wilson:1975; @tanenhaus-etal:1995]. Differential and localized processing difficulty means that different inputs in context present different processing demands during comprehension, and that by and large these demands are met relatively quickly by the mind once they are presented [@levy:2008]. XXX Behavioral measures of word-by-word reading time provide experimental evidence to test theories of language processing. Maze is a potentially promising method, and it's feasibility has recently increased due to the introduction of A-Maze [@boyceMazeMadeEasy2020]. We tested A-maze on a naturalistic corpora to learn whether participants could understand stories read in the demanding Maze task and whether the reaction time profiles from the Maze task matched those from other methods. To provide context, we first lay out the role of incremental processing methods in theory testing, describe a few common methods, and review some key influences on reading time.
